MSDS 7333 Case Study 06

### 2017-06-20 MSDS7333_CaseStudy06_MBaldree_BBrock_TElkins_AKelly.Rmd
Added code to 2.2

```{r}
# create weights for neighbors based on signal strength and multiple times X and Y and sum neighbors
# to get X and Y.
estXY = predXY(newSignals = onlineSummary[ , 6:12],
               newAngles = onlineSummary[ , 4],
               offlineSummary, numAngles = 3, k = 5, weighted=TRUE)
actXY = onlineSummary[ , c("posX", "posY")]
calcError(estXY, actXY)
```

***
<a id='References'>

@@

### Appendix (including function code)  
</a>
This is the code used to define the functions used within the study. It can be found under 'MSDS7333-baldree-case6-fx.r' which is included in the final submission  
```{r}
processLine = function(x)
{
  # Process a line of text returning a 11x10 matrix of tokens
  #
  # Args:
  #   x: The line of text
  #
  tokens = strsplit(x, "[;=,]")[[1]]

>>>>

Prediction based on weighted X and Y &darr;

```{r}
estXY = predXY(newSignals = onlineSummary[ , 6:12],
               newAngles = onlineSummary[, 4],
               offlineSummary, numAngles = 3, k = 5, weighted = TRUE, exp = .5)
actXY = onlineSummary[, c("posX","posY")]
calcError(estXY, actXY)
```

&darr; this is equivalent to mean SS error result of 210

```{r}
estXY = predXY(newSignals = onlineSummary[ , 6:12],
               newAngles = onlineSummary[, 4],
               offlineSummary, numAngles = 3, k = 5, weighted = TRUE, exp = .001)
actXY = onlineSummary[, c("posX","posY")]
calcError(estXY, actXY)
```

***
***

<a id='References'>

@@

### Appendix (including function code)  
</a>
This is the code used to define the functions used within the study. It can be found under 'MSDS7333-baldree-case6-fx.r' which is included in the final submission  
```{r eval = FALSE, echo=FALSE}
processLine = function(x)
{
  # Process a line of text returning a 11x10 matrix of tokens
  #
  # Args:
  #   x: The line of text
  #
  tokens = strsplit(x, "[;=,]")[[1]]
